---
title: "REAC - Reaction Time Analytics in Attention Bias Research"
author: "Tamas Smahajcsik-Szabo"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{REAC - Reaction Time Analytics in Attention Bias Research}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(tidyverse)
library(REAC)

example1 <- REAC::example
example2 <- REAC::example2

tidied_data <- shaker(example1, grouping = c("year", "subject"), gather = "trial", value = "RT")
winsorized_data <- winzer(tidied_data, grouping = c("year", "subject"), x = 0.3, y = 0.7, z = 1.5, label = "trial", value = "RT")
winsorized_data <- shaker(winsorized_data, grouping = c("year", "subject"), gather = "trial", value = "RT")
```
### Package Summary Info

The REAC package provides tools for 

* preparing your data for additional calculations related to **ABV-index** (*Attention Bias Variability*) and 

* data cleaning techniques such as winsorizing your data.

### Functions

#### the shaker() function
```{r eval = FALSE}
shaker(example, 
  grouping = c("year", "subject"), 
  gather = "trial", 
  value = "RT")
```


#### the ABV() function
```{r eval = FALSE}
ABV(example2, 
  grouping = c("year", "subject"), 
  trial = "trial", 
  bin_width = 3, 
  value = "RT", 
  label = "label", 
  type = c("Incongruent", "Congruent"), 
  ID = "subject")
```

#### the winzer() function

```{r eval = FALSE}
winzer(example, 
  grouping = c("year", "subject"), 
  x = 0.25, 
  y = 0.75, 
  z = 1.5, 
  label = "trial", 
  value = "RT")
```

## Effect of winzer() on a demo dataset

For details about the demo dataset used for this example, please see *"Example"* data. 

```{r echo=FALSE, fig.height=5, fig.show='hold', fig.width=6, message=FALSE, warning=FALSE}
ggplot(tidied_data, aes(RT)) +
  geom_histogram(fill = "cornflowerblue", color = "black", alpha = 1/4) +
  labs(
    title = "The original simulated reaction time data",
    x = "Reaction time (ms)",
    y = "Frequency (n)"
  ) +
  theme(
    text = element_text(family = "Garamond", size = 10)
  )

ggplot(winsorized_data, aes(RT)) +
  geom_histogram(fill = "cornflowerblue", color = "black", alpha = 1/4)+
  labs(
    title = "The winsorized simulated reaction time data",
    x = "Reaction time (ms)",
    y = "Frequency (n)"
  )+
  theme(
    text = element_text(family = "Garamond", size = 10)
  )

```
